### 2017-08-18 src/2_Finance.tex
Fin revision cap 1

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption{Holding time of an opened position of a high frequency trade.Source
  \cite{aldridge2009}}
  \label{fig:HFTtimes}
\end{figure}
In 2014 HFT represented nearly 50\% of equity trades in the US and more than
20\% in Europe showing a consistent fall since 2009 which was its best year. US
market revenues have fallen dramatically.  Figure~\ref{fig:HFTmarket} on the
left shows HFT trades percentage of US and Europe equity shares. The right
figure shows how revenues in US stocks have fallen the last years.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket}
  \caption{Left figure shows HFT market share in the US and Europe. Right figure
  shows revenue in the US.}
  \label{fig:HFTmarket}
\end{figure}
One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.

@@

A financial market is any marketplace where buyers and sellers participate
trading different assets such as equities, bonds, currencies and derivatives
(future or options). One of the main objectives of financial markets is to set
prices for global trade.
A financial market has many components but the most commonly used are money
markets and capital markets. Money markets are used for short-term basis,
usually for assets up to one year, for greater periods capital markets are used.
Capital markets include the stock or equity market and the bond or debt market
and their movements are the most widely followed.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.7\textwidth]{img/capitalmarkets}
  \caption{Old structure of capital markets.}
  \label{fig:capitalmarket}
\end{figure}
Figure~\ref{fig:capitalmarket} shows the typical structure of capital markets
existed from the early 1929s through much of the 1990s where the broker-dealers
played the central and most profitable role.  At the core are the exchanges or
inter-dealer networks (foreign exchange trading). Exchanges are the centralised
marketplaces for transacting.  Broker-dealers perform two functions: trading for
their own accounts and transacting for their customers. Broker-dealers use
inter-dealer brokers to quickly find the best price for a particular asset among
the network of other broker-dealers. Occasionally, broker-dealers also deal
directly with other broker-dealers, particularly for less liquid instruments.
Broker-dealers clients are institutional investors, corporate clients,
commercial clients, and high-net-worth individuals.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/capitalmarketsnow}
  \caption{Actual structure of capital markets.}
  \label{fig:capitalmarketnow}
\end{figure}

Equity market and foreign exchange market (Forex) are the most popular markets
for high frequency trading strategies. In the Equity market, stocks
such as futures and options, exchange-traded funds (ETFs) among others financial
instruments can be traded. Additionally, in the Forex market, interest rates denominated pair currencies 
such as EURUSD (Euro to UD dollar) or USDJPY (US dollar to Japanese yen) are traded. Traders of this market are diverse, some of them are
high frequency traders, long-term investors and corporations. The Forex market
used to be centralised, only commercial banks had exclusive access to
inter-dealer networks. Today, Forex market is decentralised and has become the
biggest market in terms of volume of trading. The main participants are
international banks geographically dispersed with continuous 24 hours operations
excepting weekends. Figure~\ref{fig:Forextimes} shows different market trading
hours in GMT for London, New York, Sydney and Tokyo.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/forex-trading-hours.png}
  \caption{Forex market trading hours (GMT).}
  \label{fig:Forextimes}
\end{figure}

@@

\begin{description}
\item[Market order] allows to buy or sell an asset at the current best price
whatever the price is. The transaction price is determined by the market
considering previous executed orders and volume requested.
\item[Limit order] allow to specify the price you want to buy or sell an asset.
Depending on the market conditions, this type of orders could never been executed.
\item[Stop order] are suitable for investors who are unable to monitor their
investments for a period of time. Stop order allows to specify the price that a
position should be closed called stop price. When the stop price is reached a
market order is executed, this means that market price could not be exactly the same
specified in the stop order.
\end{description}

@@

In order to determine the execution price, buyers and sellers orders are placed
in an order book which help to determine which order can be fulfilled.
Figure~\ref{fig:orderbook} illustrates how buyers and sellers are ordered. The
ask or offer price is the current lower price a seller is willing to accept for
a good. The bid price corresponds to the current highest price a buyer is
willing to pay for a good. Orders with the same price are prioritised by
arrival time and placed on top of the book.  The difference between current ask and bid
price is called spread and their average is called mid-price.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{img/orderbook}
  \caption{Order book. Buyers and sellers are ordered according to the bid or
  ask price and the market determines the mid-price and transacted volume.}
  \label{fig:orderbook}
\end{figure}
Today, order books are available and they are a popular source of study among
researchers. The mid-price and spread modelling are some of the
problems related with this area.

@@

EMH is related with two approaches to investment analysis: fundamental and technical analysis. Fundamental analysts base their predictions of stock price behaviour on fundamental factors such as internal information of a company, its industry or the economy. Technical analysts, by contrast, consider that all this financial information is already included in the prices and believe that future stock prices can be predicted studying the historical market behaviour. A market technician bases its predictions on historical patterns of prices of volume changes.

>>>>

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTtradestime}
  \caption{Holding time of an opened position of a high frequency trade.Source
  \cite{aldridge2009}.}
  \label{fig:HFTtimes}
\end{figure}
In 2014 HFT represented nearly 50\% of equity trades in the US and more than
20\% in Europe showing a consistent fall since 2009 which was its best year. US
market revenues have fallen dramatically.  Figure~\ref{fig:HFTmarket} on the
left shows HFT trades percentage of US and Europe equity shares. The right
figure shows how revenues in US stocks have fallen the last years.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/HFTmarket}
  \caption{Left figure shows HFT market share in the US and Europe. Right figure
  shows revenue in the US. Source: TABB Group.}
  \label{fig:HFTmarket}
\end{figure}
One of the reasons of this fall is that exchange markets have adapted, having
now faster, more transparent and efficient market structures than before.
This has been possible due to its investment in technology enhancing
reliability and stability of transactions. Even though this fall, HFT is still a major component of regulated markets and
will probably remain as a topic of interest for researchers in the near future.

@@

A financial market is any marketplace where buyers and sellers participate
trading different assets such as equities, bonds, currencies and derivatives
(future or options). One of the main objectives of financial markets is to set
prices for global trade.
A financial market has many components but the most commonly used are money
markets and capital markets. Money markets are used for short-term basis,
usually for assets up to one year, for greater periods capital markets are used.
Capital markets include the stock or equity market and the bond or debt market
and their movements are the most widely followed \cite{aldridge2009}.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.7\textwidth]{img/capitalmarkets}
  \caption{Old structure of capital markets. Source \cite{aldridge2009}.}
  \label{fig:capitalmarket}
\end{figure}
Figure~\ref{fig:capitalmarket} shows the typical structure of capital markets
existed from the early 1929s through much of the 1990s where the broker-dealers
played the central and most profitable role.  At the core are the exchanges or
inter-dealer networks (foreign exchange trading). Exchanges are the centralised
marketplaces for transacting.  Broker-dealers perform two functions: trading for
their own accounts and transacting for their customers. Broker-dealers use
inter-dealer brokers to quickly find the best price for a particular asset among
the network of other broker-dealers. Occasionally, broker-dealers also deal
directly with other broker-dealers, particularly for less liquid instruments.
Broker-dealers clients are institutional investors, corporate clients,
commercial clients, and high-net-worth individuals \cite{aldridge2009}.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/capitalmarketsnow}
  \caption{Actual structure of capital markets. Source \cite{aldridge2009}.}
  \label{fig:capitalmarketnow}
\end{figure}

Equity market and foreign exchange market (Forex) are the most popular markets
for high frequency trading strategies \cite{genccay2001introduction}. In the
Equity market, stocks such as futures and options, exchange-traded funds (ETFs)
among others financial instruments can be traded. Additionally, in the Forex
market, interest rates denominated pair currencies such as EURUSD (Euro to UD
dollar) or USDJPY (US dollar to Japanese yen) are traded. Traders of this
market are diverse, some of them are high frequency traders, long-term
investors and corporations. The Forex market used to be centralised, only
commercial banks had exclusive access to inter-dealer networks. Today, Forex
market is decentralised and has become the biggest market in terms of volume of
trading. The main participants are international banks geographically dispersed
with continuous 24 hours operations excepting weekends.
Figure~\ref{fig:Forextimes} shows different market trading hours in GMT for
London, New York, Sydney and Tokyo.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/forex-trading-hours.png}
  \caption{Forex market trading hours (GMT). Source \cite{dailyprice}.}
  \label{fig:Forextimes}
\end{figure}

@@

\begin{description}
\item[Market order] allows to buy or sell an asset at the current best price
whatever the price is. The transaction price is determined by the market
considering previous executed orders and volume requested.
\item[Limit order] allow to specify the price you want to buy or sell an asset.
Depending on the market conditions, this type of orders could never been executed.
\item[Stop order] are suitable for investors who are unable to monitor their
investments for a period of time. Stop order allows to specify the price that a
position should be closed; this price is called stop price. When the stop price
is reached a market order is executed, this means that market price could not be
exactly the same specified in the stop order.
\end{description}

@@

In order to determine the execution price, buyers and sellers orders are placed
in an order book which help to determine which order can be fulfilled.
Figure~\ref{fig:orderbook} illustrates how buyers and sellers are ordered. The
ask or offer price is the current lower price a seller is willing to accept for
a good. The bid price corresponds to the current highest price a buyer is
willing to pay for a good. Orders with the same price are prioritised by
arrival time and placed on top of the book.  The difference between current ask
and bid price is called spread and their average is called mid-price
\cite{bouchaud2002statistical}.

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.5\textwidth]{img/orderbook}
  \caption{Order book. Buyers and sellers are ordered according to the bid or
ask price and the market determines the mid-price and transacted volume. Source
\cite{gould2013limit}.}
  \label{fig:orderbook}
\end{figure}
Today, order books are available and they are a popular source of study among
researchers. The mid-price and spread modelling are some of the
problems related with this area.

@@

EMH is related with two approaches to investment analysis: fundamental and
technical analysis. Fundamental analysts base their predictions of stock price
behaviour on fundamental factors such as internal information of a company, its
industry or the economy. Technical analysts, by contrast, consider that all
this financial information is already included in the prices and believe that
future stock prices can be predicted studying the historical market behaviour.
A market technician bases his predictions on historical patterns of prices of
volume changes.
